DRAFT: v5 \\ Vibration Characterisation of Strollers and\\ Cargo Bicycles for Transporting Infants\\ \vspace{2mm} \large{Including Recommendations for Users, Designers, Manufacturers, and Researchers} \\

### 2025-03-03 main.tex
Version 5.

\usepackage{amsmath}  % extra math features
\usepackage{booktabs}  % nice tables
\usepackage{draftwatermark}  % use [nostamp] to disable
\usepackage{fancyhdr}
\usepackage[margin=25mm]{geometry}
\usepackage{graphicx} % required for inserting images
\usepackage{hyperref} % clickable hyperlinks
\usepackage{multirow}  % pandas to_latex() uses this
\usepackage{siunitx}  % use for all units
\usepackage{subcaption}  % for subfigures

@@

% watermark settings
\SetWatermarkColor[gray]{0.92}
\SetWatermarkText{Non-disclosure}
\SetWatermarkScale{5}

@@

\title{
  DRAFT: v4 \\
  Vibration Characterisation of Strollers and\\
  Cargo Bicycles for Transporting Infants\\
  \vspace{2mm}
  \large{Including Recommendations for Users, Designers, Manufacturers, and Researchers} \\
  \vspace{2mm}
  \large{Prepared for VeiligheidNL}
}
% Gabriele as first, Jason as last, alphabetical for intermediate (discuss in meeting if other method desired
\author{
Gabriele Dell'Orto \and
Brecht Daams \and
Riender Happee \and
Georgios Papaioannou \and
Arjo J. Loeve \and
Jesper Meijerink \and
Thomas Valk \and
Jason K. Moore~\footnote{corresponding author: j.k.moore@tudelft.nl, +31 (0)15 278 3556}
}

@@

\color{red}
\section*{\centering Notice}
%
This draft report is shared by TU Delft and VeiligheidNL with a number of
societal, industrial and, scientific parties. We aim to submit this to a journal
at the end of February 2025. Your feedback will be appreciated.
\\ \\
This report is shared under NON-DISCLOSURE. If you receive this report you may
share and discuss it with colleagues but do not distribute it further without
our permission. Do not place this document anywhere on internet and do not cite
this version.

@@

\subsection{Postures}
%
All tested systems provided full support of back and head and allowed usage in
lying or at least reclined postures. Nine month old infants would be able to sit
erect but will often rest their heads or be asleep. Although sitting upright is
the best posture for children who can sit upright, a more reclined posture was
tested because this allowed measurement of vibration at the head-seat interface
while the head was always supported by the headrest. We tested all systems with
horizontal or reclined postures. The inclination angle with respect to the
ground is listed in Table~\ref{tab:baby-posture} for each condition tested.
%
\begin{table}
  \centering
  \caption{Inclination angles of the IMUs ``Seat Head'' and ``Seat Pan'', per
  each tested configuration. We report the angles defined by the axis of the
  human body reference system (a reference system connected to the dummy, whose
  z-axis is aligned with the body spine and x-axis points to the front of the
  body) and the ground plane. An angle 90~\si{\degree} indicates supine posture (lying horizontally),
  -90~\si{\degree} indicates recumbent posture, and 0~\si{\degree} means erect
  posture.}
\begin{tabular}{lllrrr}
\toprule
 &  &  & & \multicolumn{2}{c}{Inclination angle [deg]}  \\
Vehicle Type & Model & Dummy & Baby seat & Seat Head & Seat Pan\\
\midrule
\multirow[t]{6}{*}{Cargo Bicycle} & \multirow[t]{3}{*}{Urban Arrow} & 0 mo & Maxi-Cosi X Joolz & 49
& -43 \\
 &  & 3 mo & Maxi-Cosi X Joolz & 49 & -43 \\
 &  & 3 mo & Melia & 26 & -28 \\
\cline{2-6}
 & \multirow[t]{3}{*}{Keiler} & 0 mo & Maxi-Cosi X Joolz & 49 & -43 \\
 &  & 3 mo & Maxi-Cosi X Joolz & 49 & -43 \\
 &  & 3 mo & Melia & 26 & -28 \\
\cline{1-6} \cline{2-6}
\multirow[t]{5}{*}{Stroller} & Maxi-Cosi Street Plus & 0 mo & Baby cot & 90 & 90\\
\cline{2-6}
 & Maxi-Cosi Street Plus & 9 mo & Baby seat & 50 & -40 \\
\cline{2-6}
 & Babyzen YOYO 0+ & 0 mo & Baby cot & 78 & 78 \\
\cline{2-6}
& Babyzen YOYO 0+ & 9 mo & Baby seat & 45 & -41 \\
\cline{2-6}
& Bugaboo Fox 5 & 0 mo & Baby cot & 90 & 90 \\
\cline{2-6}
 & Bugaboo Fox 5 & 9 mo & Baby seat & 41 & -24\\
\bottomrule
\end{tabular}
  \label{tab:baby-posture}
\end{table}

@@

    used as benchmark.

@@

\begin{table}[!h]

@@

\newpage
\section{Vehicle Statistical Comparisons}
\label{app:compare}
%
Tukey Range Test multiple comparison plots. Horizontal lines indicate 95\%
confidence intervals. Non-overlapping confidence intervals indicate a
significant difference.
%
\begin{figure}[!h]
  \centering
  \subcaptionbox{}{
  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-stroller-Cobblestones.png}}
  \subcaptionbox{}{
  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-stroller-Paver Bricks.png}}
  \subcaptionbox{}{
  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-stroller-Sidewalk Pavers.png}}
  \subcaptionbox{}{
  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-stroller-Sidewalk Slabs.png}}
  \subcaptionbox{}{
  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-stroller-Tarmac.png}}
  \caption{Tukey Comparison Plots for the Strollers}
  \label{fig:tukey-stroller}
\end{figure}
%
\begin{figure}[!h]
  \centering
  \subcaptionbox{}{
  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-bicycle-Paver Bricks-Low.png}}
  \subcaptionbox{}{
  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-bicycle-Tarmac-Low.png}}
  \subcaptionbox{}{
  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-bicycle-Paver Bricks-High.png}}
  \subcaptionbox{}{
  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-bicycle-Tarmac-High.png}}
  \caption{Tukey Comparison Plots for the Cargo Bicycles}
  \label{fig:tukey-bicycle}
\end{figure}

>>>>

\usepackage{amsmath}  % extra math features
\usepackage{booktabs}  % nice tables
%\usepackage{draftwatermark}  % use [nostamp] to disable
\usepackage{fancyhdr}
\usepackage[margin=25mm]{geometry}
\usepackage{graphicx} % required for inserting images
\usepackage{hyperref} % clickable hyperlinks
\usepackage{multirow}  % pandas to_latex() uses this
\usepackage{siunitx}  % use for all units
\usepackage{subcaption}  % for subfigures

@@

% watermark settings
%\SetWatermarkColor[gray]{0.92}
%\SetWatermarkText{Non-disclosure}
%\SetWatermarkScale{5}

@@

\title{
  DRAFT: v5 \\
  Vibration Characterisation of Strollers and\\
  Cargo Bicycles for Transporting Infants\\
  \vspace{2mm}
  \large{Including Recommendations for Users, Designers, Manufacturers, and Researchers} \\
}
% Gabriele as first, Jason as last, alphabetical for intermediate (discuss in meeting if other method desired
\author{
Gabriele Dell'Orto \and
Brecht Daams \and
Riender Happee \and
Georgios Papaioannou \and
Arjo J. Loeve \and
Jesper Meijerink \and
Thomas Valk \and
Jason K. Moore\footnote{corresponding author: j.k.moore@tudelft.nl, +31 (0)15 278 3556}
}

@@

\color{red}
\section*{\centering Notice}
%
This draft report is not yet peer reviewed and is subject to change with
revisions. These results are preliminary, so we do not recommend relying on them
until a supporting peer reviewed paper is published.

@@

\subsection{Postures}
%
All tested systems provided full support of back and head and allowed usage in
lying or at least reclined postures. Nine month old infants would be able to sit
erect but will often rest their heads or be asleep. Although sitting upright is
the best posture for children who can sit upright, a more reclined posture was
tested because this allowed measurement of vibration at the head-seat interface
while the head was always supported by the headrest. We tested all systems with
horizontal or reclined postures. The inclination angle with respect to the
ground is listed in Table~\ref{tab:baby-posture} for each condition tested.
%
\begin{table}
  \centering
  \caption{Inclination angles of the IMUs ``Seat Head'' and ``Seat Pan'', per
  each tested configuration. %We report the angles defined by the axis of the human body reference system (a reference system connected to the dummy, whose z-axis is aligned with the body spine and x-axis points to the front of the body) and the ground plane. 
  For the head 0~\si{\degree} means erect posture, and positive angles represent rearward head rotation with 90~\si{\degree} indicating a fully  supine posture (lying horizontally). For the seat pan I STILL DONT UNDERSTAND especially the -28 for Melia.}
\begin{tabular}{lllrrr}
\toprule
 &  &  & & \multicolumn{2}{c}{Inclination angle [deg]}  \\
Vehicle Type & Model & Dummy & Baby seat (facing direction)& Seat Head & Seat Pan\\
\midrule
\multirow[t]{6}{*}{Cargo Bicycle} & \multirow[t]{3}{*}{Urban Arrow} & 0 mo & Maxi-Cosi X Joolz (RF)& 41
& 2 \\
 &  & 3 mo & Maxi-Cosi X Joolz (RF)& 41 & 2 \\
 &  & 3 mo & Melia (FF)& 64 & 2 \\
\cline{2-6}
 & \multirow[t]{3}{*}{Keiler} & 0 mo & Maxi-Cosi X Joolz (RF)& 41 & 2 \\
 &  & 3 mo & Maxi-Cosi X Joolz (RF)& 49 & -43 \\
 &  & 3 mo & Melia (FF)& 64 & 2 \\
\cline{1-6} \cline{2-6}
\multirow[t]{5}{*}{Stroller} & Maxi-Cosi Street Plus & 0 mo & Baby cot (RF)& 0 & 0\\
\cline{2-6}
 & Maxi-Cosi Street Plus & 9 mo & Baby seat (FF)& 40 & 10 \\
\cline{2-6}
 & Babyzen YOYO 0+ & 0 mo & Baby cot (RF)& 12 & 12 \\
\cline{2-6}
& Babyzen YOYO 6+ & 9 mo & Baby seat (FF)& 45 & 4 \\
\cline{2-6}
& Bugaboo Fox 5 & 0 mo & Baby cot (RF)& 0 & 0 \\
\cline{2-6}
 & Bugaboo Fox 5 & 9 mo & Baby seat (FF) & 49 & 24\\
\bottomrule
\end{tabular}
  \label{tab:baby-posture}
\end{table}

@@

    used as a benchmark.

@@

\begin{table}[!ht]

@@

\newpage
\section{Vehicle Statistical Comparisons}
\label{app:compare}
%
Tukey Range Test multiple comparison plots. Horizontal lines indicate 95\%
confidence intervals. Non-overlapping confidence intervals indicate a
significant difference.
%
\begin{figure}[!ht]
  \centering
  \subcaptionbox{}{
  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-stroller-Cobblestones.png}}
  \subcaptionbox{}{
  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-stroller-Paver Bricks.png}}
  \subcaptionbox{}{
  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-stroller-Sidewalk Pavers.png}}
  \subcaptionbox{}{
  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-stroller-Sidewalk Slabs.png}}
  \subcaptionbox{}{
  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-stroller-Tarmac.png}}
  \caption{Tukey Comparison Plots for the Strollers}
  \label{fig:tukey-stroller}
\end{figure}
%
\begin{figure}[!ht]
  \centering
  \subcaptionbox{}{
  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-bicycle-Paver Bricks-Low.png}}
  \subcaptionbox{}{
  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-bicycle-Tarmac-Low.png}}
  \subcaptionbox{}{
  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-bicycle-Paver Bricks-High.png}}
  \subcaptionbox{}{
  \includegraphics[width=90mm]{fig/tukey-SeatBotacc_ver-bicycle-Tarmac-High.png}}
  \caption{Tukey Comparison Plots for the Cargo Bicycles}
  \label{fig:tukey-bicycle}
\end{figure}
